### 2024-10-11 manuscript.tex
Update metadata.yaml [ci skip]
This build is based on
https://github.com/pivlab/annual_review_of_biomedical_data_science/commit/6a128344693fc244f80501a6df4346fbd4e190e5.

This commit was created by the following CI build and job:
https://github.com/pivlab/annual_review_of_biomedical_data_science/commit/6a128344693fc244f80501a6df4346fbd4e190e5/checks
https://github.com/pivlab/annual_review_of_biomedical_data_science/actions/runs/11285124590

This manuscript
(\href{https://pivlab.github.io/annual_review_of_biomedical_data_science/v/d940251e024223111145d42fb373b9cc191fe474/}{permalink})
was automatically generated
from \href{https://github.com/pivlab/annual_review_of_biomedical_data_science/tree/d940251e024223111145d42fb373b9cc191fe474}{pivlab/annual\_review\_of\_biomedical\_data\_science@d940251}
on October 11, 2024.

@@

\begin{itemize}
\item
  \textbf{Marc Subirana-Granés}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3934-839X}{0000-0003-3934-839X}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/msubirana}{msubirana}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/msubirana20}{msubirana20}
  Department of Biomedical Informatics, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Jill Hoffman}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-2690-2593}{0000-0002-2690-2593}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/jillhoffman}{jillhoffman}
  Department of Biomedical Informatics, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Haoyu Zhang}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0009-0005-6025-0217}{0009-0005-6025-0217}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/haoyu-zc}{haoyu-zc}
  Department of Biomedical Informatics, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Christina Akirtava}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-7587-2303}{0000-0001-7587-2303}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/bio2data}{bio2data}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/bio2data}{bio2data}
  Department of Biochemistry and Molecular Genetics, RNA Bioscience Initiative, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Sutanu Nandi}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0009-0001-5887-999X}{0009-0001-5887-999X}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/snandi-DS}{snandi-DS}
  Department of Pharmacology, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Kevin Fotso}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/kf-cuanschutz}{kf-cuanschutz}
  Office of Information Technology, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Milton Pividori}
  \textsuperscript{\protect\hyperlink{correspondence}{✉}}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-3035-4403}{0000-0002-3035-4403}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/miltondp}{miltondp}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/miltondp}{miltondp}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://genomic.social/@miltondp}{@miltondp@genomic.social}
  Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA; Colorado Center for Personalized Medicine, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
  · Funded by The National Human Genome Research Institute (K99/R00 HG011898); The Eunice Kennedy Shriver National Institute of Child Health and Human Development (R01 HD109765)
\end{itemize}

>>>>

This manuscript
(\href{https://pivlab.github.io/annual_review_of_biomedical_data_science/v/6a128344693fc244f80501a6df4346fbd4e190e5/}{permalink})
was automatically generated
from \href{https://github.com/pivlab/annual_review_of_biomedical_data_science/tree/6a128344693fc244f80501a6df4346fbd4e190e5}{pivlab/annual\_review\_of\_biomedical\_data\_science@6a12834}
on October 11, 2024.

@@

\begin{itemize}
\item
  \textbf{Marc Subirana-Granés}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3934-839X}{0000-0003-3934-839X}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/msubirana}{msubirana}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/msubirana20}{msubirana20}
  Department of Biomedical Informatics, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Jill Hoffman}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-2690-2593}{0000-0002-2690-2593}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/jillhoffman}{jillhoffman}
  Department of Biomedical Informatics, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Haoyu Zhang}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0009-0005-6025-0217}{0009-0005-6025-0217}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/haoyu-zc}{haoyu-zc}
  Department of Biomedical Informatics, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Christina Akirtava}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-7587-2303}{0000-0001-7587-2303}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/bio2data}{bio2data}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/bio2data}{bio2data}
  Department of Biochemistry and Molecular Genetics, RNA Bioscience Initiative, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Sutanu Nandi}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0009-0001-5887-999X}{0009-0001-5887-999X}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/snandi-DS}{snandi-DS}
  Department of Pharmacology, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Kevin Fotso}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0009-0002-2196-6157}{0009-0002-2196-6157}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/kf-cuanschutz}{kf-cuanschutz}
  Office of Information Technology, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
\item
  \textbf{Milton Pividori}
  \textsuperscript{\protect\hyperlink{correspondence}{✉}}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-3035-4403}{0000-0002-3035-4403}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/miltondp}{miltondp}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/miltondp}{miltondp}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://genomic.social/@miltondp}{@miltondp@genomic.social}
  Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA; Colorado Center for Personalized Medicine, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
  · Funded by The National Human Genome Research Institute (K99/R00 HG011898); The Eunice Kennedy Shriver National Institute of Child Health and Human Development (R01 HD109765)
\end{itemize}
